Nuclear Energy: Kahan scale and Economic Political value scale

### 2024-01-31 Paper1.Rmd
counting NAs

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)
codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
joineddf$Urban <- as.factor(joineddf$urban_rural)
codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)

@@

@@

## Kahan scater plot from the CFA scores 
```{r, echo = FALSE}

@@

```{r dev = "jpg", echo=FALSE}

@@

@@

fascale_scores2

>>>>

# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
joineddf$Uppercaste <- ifelse(joineddf$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
joineddf$Male <- ifelse(joineddf$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
joineddf$Hindu <- ifelse(joineddf$religion == 'Hinduism', 1, 0)
codedmodule2$State <- as.factor(codedmodule2$State)
codedmodule2$gender <- as.factor(codedmodule2$gender)
codedmodule2$Urban <- as.factor(codedmodule2$urban_rural)
joineddf$Urban <- as.factor(joineddf$urban_rural)
codedmodule2$caste <- as.factor(codedmodule2$caste)
codedmodule2$religion <- as.factor(codedmodule2$religion)
# # Convert `caste` into binary variable 'upper' (1) vs 'non-upper' (0)
codedmodule2$Uppercaste <- ifelse(codedmodule2$caste %in% c('Brahmin', 'General'), 1, 0)
# Convert `gender` into binary variable 'male' (1) vs 'female' (0)
codedmodule2$Male <- ifelse(codedmodule2$gender == 'Male', 1, 0)
# Convert `religion` into binary variable 'Hinduism' (1) vs 'Non-Hinduism' (0)
codedmodule2$Hindu <- ifelse(codedmodule2$religion == 'Hinduism', 1, 0)
joineddf$State <- as.factor(joineddf$State)

@@

state_counts <- alldemos %>%
  group_by(State) %>%
  summarise(Count = n())

@@

\newpage
# Na counting

relevant <- codedmodule2 %>%
  dplyr::select(starts_with(c("Risky", "Ben","K_", "WEALTHLIM","MECHANISATION","DECISIONDECEN","DECISIONCEN","INDUSTRYLARGE","INDUSTRYSMALL","ECONOMYGLOBAL","ECONOMYLOCAL", "ENVOVERDEV","DEVOVERENV","OWNERPVT","OWNERNOREG","OWNERPUB", "OWNERREG","DISPLACENUCLEAR",  "POLLUTENUCLEAR", "HEALTHNUCLEAR", "JOBSNUCLEAR", "BEAUTYNUCLEAR", "PRIDENUCLEAR", "NPRIDENUCLEAR", "DEVNUCLEAR", "PROSPERNUCLEAR", "RELYNUCLEAR", "Uppercaste", "Male", "Hindu", "Urban", "State","age")))%>%
  dplyr::select(!starts_with(c("Risky_IND","Ben_IND")))%>%
  mutate_at(vars(age), funs(case_when(. == "18-24 years old" ~ 1, 
                                      . == "25-34 years old" ~ 2,
                                      . ==  "35-44 years old" ~3,
                                      . == "45-54 years old" ~ 4,
                                      . == "55-64 years old" ~ 5,
                                      . == "65-74 years old" ~ 6,
                                      . == "75 years or older" ~ 7)))

relevant_na <- relevant %>% summarise_all(~sum(is.na(.)))

str(relevant)
str(relevant_na)
```

\newpage
## Kahan scater plot from the CFA scores 
```{r, echo = FALSE}

@@

@@

state_counts2 <- fascale_scores %>%
  group_by(State) %>%
  summarise(Count = n())

@@
